---
title: "Information about peaks"
author: "Saskia Freytag"
date: "10/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rtracklayer)
```

```{r}
peaks <- readRDS("snATACseq/processed_data/cell_type_atac_peaks_filtered_anno_stage_CRE_gr.Rds")
all_peaks <- unlist(as(peaks, "GRangesList"))
all_peaks <- reduce(all_peaks)

length(all_peaks)
```

## Shared between all cell types

```{r cars}
ind_all <- lapply(peaks, function(x) unique(findOverlaps(x, all_peaks)@to))
tab_all <- table(unlist(ind_all))

in_all <- sum(tab_all==9)/length(all_peaks)*100
in_half <- sum(tab_all>=4)/length(all_peaks)*100
in_two <- sum(tab_all>=2)/length(all_peaks)*100
unique_celltype <- sum(tab_all==1)/length(all_peaks)*100
```

Roughly `r round(in_all, 2)`\% OCRs are found in all cell types, roughly 
`r round(in_half, 2)`\% OCRs are found in 4 or more cell types and roughly
`r round(in_two, 2)`\% OCRs are found in 2 or more cell types.

Roughly `r round(unique_celltype, 2)` \% OCRs are unique to a celltype.

## Shared between developmental stages

```{r}
stages <- c("Fetal", "Neonatal", "Infancy", "Childhood", "Adolescence", "Adult")
peaks_ind <- lapply(peaks, function(x) 
    apply(x@elementMetadata[,stages], 1, function(y)
    sum(y))==0)
in_stages <- lapply(1:length(peaks), function(x) 
    apply(peaks[[x]]@elementMetadata[!peaks_ind[[x]],stages], 1, function(y)
    sum(y)))

in_all <- mean(sapply(in_stages, function(x) sum(x==max(x))/length(x)))*100
in_half <- mean(sapply(in_stages, function(x) sum(x>=3)/length(x)))*100
unique_stage <-  mean(sapply(in_stages, function(x) sum(x==1)/length(x)))*100
```

On average, roughly `r round(in_all, 2)`\% OCRs are found in all stages in a cell type, 
roughly `r round(in_half, 2)`\% OCRs are found in 3 or more stages in a cell 
type.

On average, roughly `r round(unique_stage, 2)` \% OCRs are unique to a stage in
a cell type.
